%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

\usepackage{harvard}
\cfoot{\thepage}

% adjust the page margins
\usepackage[scale=0.75]{geometry}
\sethintscolumntowidth{04/19 -- present}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvheadnamewidth}{10cm}            % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Konan}{Hara}
\title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{7-3-1 Hongo, Bunkyo-ku}{Tokyo 113-0033}{Japan}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{+81-90-8507-1062}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\phone[fixed]{+81-3-5841-5543}
%\phone[fax]{+81-3-5841-3303}
\email{hara.konan@gmail.com}                               % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\social[linkedin]{john.doe}                        % optional, remove / comment the line if not wanted
%\social[xing]{john\_doe}                           % optional, remove / comment the line if not wanted
%\social[twitter]{jdoe}                             % optional, remove / comment the line if not wanted
\social[github]{harakonan}                              % optional, remove / comment the line if not wanted
%\social[gitlab]{jdoe}                              % optional, remove / comment the line if not wanted
%\social[skype]{jdoe}                               % optional, remove / comment the line if not wanted
\extrainfo{updated \today}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2019}{Ph.D.}{Graduate School of Medicine, The University of Tokyo}{Japan}{}{}
\cventry{2013}{M.D.}{Faculty of Medicine, The University of Tokyo}{Japan}{}{}  % arguments 3 to 6 can be left empty
\cventry{2013}{B.A.}{Faculty of Medicine, The University of Tokyo}{Japan}{}{}

\section{Research Interests}
\cvlistitem{Econometrics}
\cvlistitem{Biostatistics and Epidemiology}
\cvlistitem{Health Economics}
\cvlistitem{Behavioral Economics}

\section{Qualification}
\cvitem{2013}{Medical Doctor in Japan}

\section{Appointments and Affiliations}

\subsection{Academic Positions}
\cventry{04/19 -- present}{Project Researcher}{Graduate School of Economics, The University of Tokyo}{Tokyo}{Japan}{}
\cventry{04/19 -- present}{Part-time Researcher}{TXP Medical Co., Ltd.}{Tokyo}{Japan}{}
\cventry{04/19 -- present}{Part-time Researcher}{Department of Hematology, Tokyo Metropolitan Cancer and Infectious Diseases Center Komagome Hospital}{Tokyo}{Japan}{}
\cventry{07/17 -- 03/19}{Project Researcher}{Department of Health Policy, Graduate School of Medicine, The University of Tokyo}{Tokyo}{Japan}{}

\subsection{Appointments at Hospitals}
\cventry{07/16 -- present}{Nephrologist}{Chiba Aiyukai Kinen Hospital}{Chiba}{Japan}{}
\cventry{01/16 -- 06/16}{Nephrologist}{Ageo Central General Hospital Eight Nine Clinic}{Saitama}{Japan}{}
\cventry{04/15 -- 12/15}{Physician}{Nishimura Heart Clinic}{Saitama}{Japan}{}
\cventry{04/14 -- 03/15}{Resident}{The University of Tokyo Hospital}{Tokyo}{Japan}{}
\cventry{04/13 -- 03/14}{Resident}{The Fraternity Memorial Hospital}{Tokyo}{Japan}{}

\section{Research Experience}
\cvitem{08/17 -- 03/19}{Research Assistant for Hidehiko Ichimura, Graduate School of Economics, The University of Tokyo}
\cvitem{02/17 -- 03/17}{Research Assistant for Hajime Sato, National Institute of Public Health}
\cvitem{07/16 -- 03/17}{Research Assistant for Yuichi Tei, Graduate School of Engineering, The University of Tokyo}

\section{Honors and Awards}
\cvitem{2014}{Award of Excellence, Grand Round of Internal Medicine, The University of Tokyo Hospital}

\section{Grants}
\cvitem{2019}{Investigator, Elucidation of regulatory mechanisms for latent infection in progenitor cells and molecular mechanisms for virus reactivation along with cell differentiation (PI: Ayumi Taguchi), Japan Agency for Medical Research and Development (AMED)}
\cvitem{2018}{Investigator, Self-Managing Healthy Society (PI: Yuichi Tei), Japan Science and Technology Agency (JST)}

\section{Computer Skills}
\cvcomputer{Data Science}{R, Python, Stata}{RDBMS}{Oracle SQL, MySQL}
\cvcomputer{Documentation}{LaTeX, GFM, R markdown}{Others}{Unix}

\section{Personal Information}
\cvitem{Citizenship}{Japan}
\cvitem{Language}{English (fluent), Japanese (native)}

\section{Dissertation}
\cvitem{Title}{\emph{Claims-based algorithms for common chronic conditions were investigated using regularly collected data in Japan}}
\cvitem{Supervisor}{Yasuki Kobayashi}
\cvitem{Description}{The literature of claims-based algorithm (CBA) has two features to be refined: the use of a chart review as a source of the gold standard; the procedure of searching for a fine-tuned CBA based on existing knowledge regarding target conditions. The first feature limits the population to which the CBA can be applied and the second makes the CBA construction procedure to be an overly complicated and cumbersome matter. Moreover, the burden of reviewing charts and searching for a fine-tuned CBA lead to a slow establishment of acceptable CBAs because it discourages researchers from CBA studies. The sluggish establishment of usable CBAs can be a big issue as the codes recorded in the claims for transmitting information about patients are supposed to change periodically. The dissertation focused on CBAs for identifying patients with three common chronic medical conditions, hypertension, diabetes, and dyslipidemia, and (1) demonstrated the usefulness of health screening results as the source of gold standard; (2) showed the power of statistical learning methods to develop an efficient CBA construction procedure; (3) proposed a course of action for an efficient CBA research. I believe that the series of techniques evaluated in the study should become essential in future CBA research.}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file                 

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

\section{Working Papers}
\cvitem{[1]}{Yuki Ito, Konan Hara, and Jun Tomio. Perception of Generic Drugs and Willingness-to-pay: A Survey-based Study. 2019.}
\cvitem{[2]}{Takuya Shimizuguchi, Noritaka Sekiya, Konan Hara, Ayumi Taguchi, Yujiro Nakajima, Yu Miyake, Yukiko Shibata, Kentaro Taguchi, Hiroaki Ogawa, Kei Ito, Keiji Nihei, and Katsuyuki Karasawa. Radiation therapy and risk of herpes zoster in patients with cancer. 2019.}
\cvitem{[3]}{Ayumi Taguchi, Konan Hara, Jun Tomio, Kei Kawana, Tomoki Tanaka, Satoshi Baba, Akira Kawata, Satoko Eguchi, Katsuyuki Adachi, Takeshi Nagamatsu, Katsutoshi Oda, Yutaka Osuga, and Tomoyuki Fujii. Application of a multistate Markov model to predict the prognosis of high-risk human papillomavirus-related cervical lesions. 2019.}
\cvitem{[4]}{Satoshi Kaito, Yujiro Nakajima, Konan Hara, Takashi Toya, Tetsuya Nishida, Naoyuki Uchida, Takahiro Fukuda, Yukiyasu Ozawa, Heiwa Kanamori, Junya Kanda, Yoshiko Atsuta, Masao Ogata, Ayumi Taguchi, and Kazuteru Ohashi. Heterogeneous impact of cytomegalovirus reactivation on non-relapse mortality in hematopoietic stem cell transplantation. 2019. \emph{Revision Requested, Blood Advances}.}
\cvitem{[5]}{Yuki Ito, Konan Hara, and Yasuki Kobayashi. The Effect of Inertia on Brand-name vs. Generic Drug Choice. 2019. \emph{Revision Requested 2nd Round, Journal of Economic Behavior and Organization}.}
\cvitem{[6]}{Yuki Ito, Konan Hara, Byung-Kwang Yoo, Jun Tomio, and Yasuki Kobayashi. Can income-based co-payment rates improve disparity in access to brand-name drugs? Evidence from Japan’s elderly population. 2019. \emph{Forthcoming, BMC Health Services Research}.}

\section{Conference Presentations}
\cvitem{2017}{International Health Economics Association 12th World Congress; Japanese Society of Public Health Annual Meeting}
\cvitem{2015}{Japanese Society of Public Health Annual Meeting}


% \clearpage
% %-----       letter       ---------------------------------------------------------
% % recipient data
% \recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
% \date{January 01, 1984}
% \opening{Dear Sir or Madam,}
% \closing{Yours faithfully,}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
% \makelettertitle

% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.

% Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.

% Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.

% Albert Einstein discovered that $e=mc^2$ in 1905.

% \[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]

% \makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
